MSOA domestic Electricity and Gas maps

### 2021-08-26 MSOA-domestic-Elec-and-Gas.Rmd
Adding the layover maps and histograms to be used in the analysis

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Map with Overlay
```{r Check leaflet for dom elec consumption}
library(leaflet)

@@

              label =~(popup_text),
             ##labelOptions -labelOptions(
               ##style = list("font-weight"= "normal", padding ="2px 2px"),
               ##direction ="auto"),

>>>>

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```

####Map with Overlay
```{r Check leaflet for dom elec consumption}
library(leaflet)

@@
